RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
abstract

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate them.
This paper serves to evaluate to which extend each requirement is satisfied by each of these constraint languages.
We take reasoning into account as an important pre-validation step and map constraints to DL
%, and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
%We classify constraints according to a developed classification mechanism for constraints.
in order to show that each constraint can be mapped to an ontology describing RDF constraints generically.
%If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
%If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.

>>>>

\begin{abstract}
There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
By contributing to the W3C and the DCMI working groups on RDF validation, we identified many RDF validation requirements
and initiated an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
there is no standard way to formulate them.
This paper serves to evaluate to which extend each requirement is satisfied by each of these constraint languages.
We take reasoning into account as an important pre-validation step and map constraints to DL
%, and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
%We classify constraints according to a developed classification mechanism for constraints.
in order to show that each constraint can be mapped to an ontology describing RDF constraints generically.
%If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
%If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.
